---
title: "The Thickness of Collagen Membrane"
author: "Frank (Bo-Jiang Lin)"
date: "2022-08-28"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## GitHub Documents

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

## Including Code

### 1. Configure the necessary environment and packages

The analysis is powered by `r version[['version.string']]`.
```{r package, message=FALSE}
library(readxl)
library(UsingR)
library(lessR)
library(ggplot2)
library(knitr)
```

### 2. Read Data

```{r excel, echo= FALSE}
collagen <- read_excel("E:/OneDrive/Tokyo Metropolitan University/Collagen Membrane.xlsx", sheet = 2)
colnames(collagen)[which(names(collagen)=="UnCompressed Thickness (μm)")] <- "UnCompressed_Thickness"
colnames(collagen)[which(names(collagen)=="Total solution quantity (ml)")] <- "Total_solution_quantity"
#eliminate the physical unit label from the column names

collagen$Date <- as.Date(format(collagen$Date, "%Y-%m-%d"))
#Parse the date and time into date only

exp_date <- as.Date("2022-08-28")
collagen_Frank <- subset.data.frame(collagen, Person == "Frank" & Date == exp_date)
collagen_1ml <- subset.data.frame(collagen, Total_solution_quantity==1 & Person != "Oyamasan")
kable(head(collagen,5))
```

### 3. Exploratory Data Analysis for `r exp_date` data

#### Descriptive Statistics on the `r exp_date` data

```{r description, echo= FALSE}
collagen_Frank_mean <- aggregate(collagen_Frank[c("Total_solution_quantity","UnCompressed_Thickness")],list(collagen_Frank$Total_solution_quantity),mean)
collagen_Frank_sd <- aggregate(collagen_Frank[c("Total_solution_quantity","UnCompressed_Thickness")],list(collagen_Frank$Total_solution_quantity),sd)
kable(collagen_Frank_mean)
```

#### Check whether the `r exp_date` data is normal distribution
```{r normal test}
summary(collagen$UnCompressed_Thickness)
#Creat a table

normal <- shapiro.test(collagen$UnCompressed_Thickness)
normal
```

##### The `r exp_date` data shows p-value = `r round(normal$p.value,2)``r if(normal$p.value < 0.1){" < 0.1. It represent that the data distrubute abnormally and need to be fitted by distribution test."}else{" >= 0.1. It represent that the data distrubute normally and ready for further test."}`.

```{r t test}
comparison <- t.test(collagen_Frank$UnCompressed_Thickness ~ collagen_Frank$Total_solution_quantity)
comparison
```

##### The `r exp_date` data shows p-value is `r round(comparison$p.value,2)`  `r if(comparison$p.value > 0.05){" >= 0.05 which means we accept the H0 hypothesis."}else{"< 0.5 which means we reject the H0 hypothesis and accept the H1 hypothesis."}`

### 4. Reproducibility
```{r EDA for reproducibility, echo= FALSE}
collagen_1ml_mean <- aggregate(collagen_1ml[c("Total_solution_quantity","UnCompressed_Thickness")],list(collagen_1ml$Person),mean)
collagen_1ml_sd <- aggregate(collagen_1ml[c("Total_solution_quantity","UnCompressed_Thickness")],list(collagen_1ml$Person),sd)
kable(collagen_1ml_mean)
```

```{r anova for reproducibility}
reproducibility <- t.test(collagen_1ml$UnCompressed_Thickness ~ collagen_1ml$Person)
reproducibility
```

##### The p-value is `r round(reproducibility$p.value,2)` which means `r if(reproducibility$p.value > 0.05){"the data reach to the consensus results while p-value is higher than 0.05."}else{"the data are aberant from the previous data because of the p-value is lower than 0.05."}`

## Including Plots

### 1. the distribution of the `r exp_date` data
```{r normal plot, echo = FALSE}
simple.eda(collagen_Frank$UnCompressed_Thickness)
```

### 2. the comparison of the `r exp_date` data
```{r comparison, echo = FALSE}
barplotcomparison <- barplot(collagen_Frank_mean$UnCompressed_Thickness ~ collagen_Frank_mean$Group.1, ylim = c(0,800))
arrows(x0 = barplotcomparison,
       y1 = collagen_Frank_mean$UnCompressed_Thickness + collagen_Frank_sd$UnCompressed_Thickness,
       y0 = collagen_Frank_mean$UnCompressed_Thickness - collagen_Frank_sd$UnCompressed_Thickness,
       angle = 90,
       code = 3,
       length = 0.1
)
```

### 3. the comparison study on the `r exp_date` data with the prvious study
```{r reproducibility, echo = FALSE}
barplotreproducibility <- barplot(collagen_1ml_mean$UnCompressed_Thickness ~ collagen_1ml_mean$Group.1, ylim = c(0,750))
arrows(x0 = barplotreproducibility, 
       y0 = collagen_1ml_mean$UnCompressed_Thickness + collagen_1ml_sd$UnCompressed_Thickness,
       y1 = collagen_1ml_mean$UnCompressed_Thickness - collagen_1ml_sd$UnCompressed_Thickness,
       angle = 90,
       code = 3,
       length = 0.1
)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
