---
title: "Collagen_Membrane_PPTx"
author: "Frank"
date: "2022-09-27"
output: powerpoint_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

-   Bullet 1
-   Bullet 2
-   Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
library(RODBC)
library(UsingR)
library(ggpubr)
library(ggplot2)
library(ggsignif)
library(dplyr)
library(ggeasy)
library(ggplot2)
library(rstatix)
```

## Set up driver info and database path

```{r access_path}
DRIVERINFO <- "Driver={Microsoft Access Driver (*.mdb, *.accdb)};"
MDBPATH <- "E:/OneDrive/文件/TMU-DESKTOP-SF2LD60.accdb"
PATH <- paste0(DRIVERINFO, "DBQ=", MDBPATH)
```

## Establish connection

```{r connection}
channel <- odbcDriverConnect(PATH)
```

## Load data into R dataframe

```{r Load}
df <- sqlQuery(channel,"SELECT * FROM CollagenMembrane;", stringsAsFactors = FALSE)
```

## Table on the Data

```{r Table}
df_data <- subset.data.frame(df,Date=="2022-11-13" | Date=="2022-10-25" | Date=="2022-10-20")
SynthesisMatrix <- df_data %>%
  group_by(`Area`) %>%
  summarise(
    count = n(),
    mean = mean(`Youngs Modulus (kPa)`, na.rm = TRUE),
    sd = sd(`Youngs Modulus (kPa)`, na.rm = TRUE),
    median = median(`Youngs Modulus (kPa)`, na.rm = TRUE),
    IQR = IQR(`Youngs Modulus (kPa)`, na.rm = TRUE),
    se = sd(`Youngs Modulus (kPa)`, na.rm = TRUE)/sqrt(n())
  )
SynthesisMatrix$Area <- factor(SynthesisMatrix$Area, levels = c("Lowest","Middle","Highest"))
SynthesisMatrix
```

## Divide into the subgroups

```{r divided}
low <- subset.data.frame(df_data, Area =="Lowest")
Mid <- subset.data.frame(df_data, Area =="Middle")
High <- subset.data.frame(df_data, Area =="Highest")
```

## Check the normality

```{r normal}
normalTest <- shapiro.test(low$`Youngs Modulus (kPa)`)
simple.eda(low$`Youngs Modulus (kPa)`)
normalTest
```
```{r}
normalTest <- shapiro.test(Mid$`Youngs Modulus (kPa)`)
simple.eda(Mid$`Youngs Modulus (kPa)`)
normalTest
```
```{r}
normalTest <- shapiro.test(High$`Youngs Modulus (kPa)`)
simple.eda(High$`Youngs Modulus (kPa)`)
normalTest
```
## Comparison

```{r}
df_data <- rename(df_data,c("Youngs"="Youngs Modulus (kPa)"))
pstat <- compare_means(`Youngs` ~ Area,data = df_data, method = "kruskal.test")
pstat
```

## Run post-hoc

```{r}
dun <- df_data %>%
  dunn_test(Youngs ~ Area, p.adjust.method="bonferroni") %>%
  add_xy_position(x="Area", fun = "mean_sd", dodge = 0.8)
dun
```


## Plot

```{r}
ggbarplot(SynthesisMatrix, x="Area", y="mean", ylab = "Youngs Modulus (kPa)", palette = "jco", label = TRUE)+ 
  geom_bar(stat="identity", position=position_dodge())+
  geom_errorbar(aes(ymin=mean-se, ymax=mean+se), width=.2, position=position_dodge(.9))+
  stat_pvalue_manual(dun, hide.ns = TRUE)+
  ggtitle("The stiffness of the compressed wedged collagen")+
  easy_center_title()+ 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),axis.line = element_line(size = 0.9), axis.ticks = element_line(size = 0.9))
```


## Close and remove channel

```{r}
close(channel)
```
