---
title: "The Thickness of Collagen Membrane"
author: "Frank (Bo-Jiang Lin)"
date: "2022-08-28"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## GitHub Documents

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

## Including Code

### 1. Configure the necessary environment and packages

The analysis is powered by `r version[['version.string']]`.
```{r package, message=FALSE}
library(readxl)
library(UsingR)
library(lessR)
library(ggplot2)
library(knitr)
library(ggsignif)
library(ggpubr)
```

### 2. Read Data

```{r excel, echo= FALSE}
collagen <- read_excel("E:/OneDrive/Tokyo Metropolitan University/Collagen Membrane/Collagen Membrane.xlsx", sheet = 2)
colnames(collagen)[which(names(collagen)=="UnCompressed Thickness (μm)")] <- "UnCompressed_Thickness"
colnames(collagen)[which(names(collagen)=="Total solution quantity (ml)")] <- "Total_solution_quantity"
colnames(collagen)[which(names(collagen)=="Youngs Modulus before compression (kPa)")] <- "Youngs_Modulus"
colnames(collagen)[which(names(collagen)=="0 day Compressed Thickness")] <- "zero_day_Compressed_Thickness"
#eliminate the physical unit label from the column names

collagen$Date <- as.Date(format(collagen$Date, "%Y-%m-%d"))
#Parse the date and time into date only

exp_date <- as.Date("2022-08-28")
collagen_Frank <- subset.data.frame(collagen, Person == "Frank"& Date == exp_date)
collagen_1ml <- subset.data.frame(collagen, Total_solution_quantity==1 & Person != "Oyamasan")
collagen_Frank_1ml <- subset.data.frame(collagen_Frank, Total_solution_quantity==1)
collagen_Frank_1.5ml <- subset.data.frame(collagen_Frank, Total_solution_quantity==1.5)
kable(collagen_Frank)
```

### 3. Exploratory Data Analysis of the uncompressed thickness for `r exp_date` data

#### Descriptive Statistics on the `r exp_date` data

```{r description, echo= FALSE}
collagen_Frank_mean <- aggregate(collagen_Frank[c("UnCompressed_Thickness","zero_day_Compressed_Thickness")],list(Quantity=collagen_Frank$Total_solution_quantity),mean,na.rm = TRUE)
collagen_Frank_sd <- aggregate(collagen_Frank[c("UnCompressed_Thickness","zero_day_Compressed_Thickness")],list(Quantity=collagen_Frank$Total_solution_quantity),sd,na.rm = TRUE)
kable(collagen_Frank_mean)
#Buffer=collagen_Frank$`Buffer (pH)`,
```


#### Check whether the `r exp_date` data is normal distribution
```{r normal test}
summary(collagen$UnCompressed_Thickness)
#Creat a table

normal <- shapiro.test(collagen$UnCompressed_Thickness)
normal
```

##### The `r exp_date` data shows p-value = `r round(normal$p.value,2)``r if(normal$p.value < 0.1){" < 0.1. It represent that the data distrubute abnormally and need to be fitted by distribution test."}else{" >= 0.1. It represent that the data distrubute normally and ready for further test."}`.

```{r f-test}
variance <- var.test(collagen_Frank$UnCompressed_Thickness ~ collagen_Frank$Total_solution_quantity)
variance
```

```{r t test}
comparison <- t.test(collagen_Frank$UnCompressed_Thickness ~ collagen_Frank$Total_solution_quantity, var.equal = TRUE)
comparison
```

##### The `r exp_date` data shows p-value is `r round(comparison$p.value,2)`  `r if(comparison$p.value > 0.05){" >= 0.05 which means we accept the H0 hypothesis."}else{"< 0.5 which means we reject the H0 hypothesis and accept the H1 hypothesis."}`

### 4. Reproducibility of uncompressed thickness 
```{r EDA for reproducibility, echo= FALSE}
collagen_1ml_mean <- aggregate(collagen_1ml[c("Total_solution_quantity","UnCompressed_Thickness","zero_day_Compressed_Thickness")],list(collagen_1ml$Person),mean)
collagen_1ml_sd <- aggregate(collagen_1ml[c("Total_solution_quantity","UnCompressed_Thickness","zero_day_Compressed_Thickness")],list(collagen_1ml$Person),sd)
kable(collagen_1ml_mean)
```

```{r f-test for reproducibility}
var.test(collagen_1ml$UnCompressed_Thickness ~ collagen_1ml$Person)
```

```{r anova for reproducibility}
reproducibility <- t.test(collagen_1ml$UnCompressed_Thickness ~ collagen_1ml$Person,var.equal=TRUE)
reproducibility
```

##### The p-value is `r round(reproducibility$p.value,2)` which means `r if(reproducibility$p.value > 0.05){"the data reach to the consensus results while p-value is higher than 0.05."}else{"the data are aberant from the previous data because of the p-value is lower than 0.05."}`

### 5. Young's Modulus of uncompressed thickness fo The `r exp_date` data

```{r youngsmodulus}
youngs_mean <- aggregate(collagen_Frank[c("Total_solution_quantity","Youngs_Modulus")],list(collagen_Frank$Total_solution_quantity),mean,na.rm = TRUE)
youngs_sd <- aggregate(collagen_Frank[c("Total_solution_quantity","Youngs_Modulus")],list(collagen_Frank$Total_solution_quantity),sd,na.rm = TRUE)
kable(youngs_mean)
```

```{r younsmodulus_norma}
normal_youngs <- shapiro.test(collagen_Frank$Youngs_Modulus)
normal_youngs
```

##### The `r exp_date` data shows p-value = `r round(normal_youngs$p.value,2)``r if(normal_youngs$p.value < 0.1){" < 0.1. It represent that the data distrubute abnormally and need to be fitted by distribution test."}else{" >= 0.1. It represent that the data distrubute normally and ready for further test."}`.

```{r youngs_f test}
youngs_var <- var.test(collagen_Frank$Youngs_Modulus ~ collagen_Frank$Total_solution_quantity)
youngs_var
```

##### The `r exp_date` data shows p-value is `r round(youngs_var$p.value,2)`  `r if(youngs_var$p.value > 0.05){" >= 0.05 which means we accept the H0 hypothesis."}else{"< 0.5 which means we reject the H0 hypothesis and accept the H1 hypothesis."}`

```{r youngs_comparison}
youngs_compar <- t.test(collagen_Frank$Youngs_Modulus ~ collagen_Frank$Total_solution_quantity, var.equal = TRUE)
youngs_compar
```

##### The `r exp_date` data shows p-value is `r round(youngs_compar$p.value,2)`  `r if(youngs_compar$p.value > 0.05){" >= 0.05 which means we accept the H0 hypothesis."}else{"< 0.5 which means we reject the H0 hypothesis and accept the H1 hypothesis."}`

### 6. Exploratory Data Analysis on the compressed thickness for the `r exp_date` data
```{r summary1mlCompressedThickness}
summary(collagen_Frank_1ml$zero_day_Compressed_Thickness)

normalcompressed <- shapiro.test(collagen_Frank_1ml$zero_day_Compressed_Thickness)
normalcompressed
```

```{r summary1.5mlCompressedThickness}
summary(collagen_Frank_1.5ml$zero_day_Compressed_Thickness)

normalcompressed <- shapiro.test(collagen_Frank_1.5ml$zero_day_Compressed_Thickness)
normalcompressed
```

### 7. Comprison study on the compressed thickness for the `r exp_date` data

```{r F test for compressionThickness}
compressed_var <- var.test(collagen_Frank$zero_day_Compressed_Thickness ~ collagen_Frank$Total_solution_quantity)
compressed_var
```

```{r comparision_compressed}
compressed_t <- t.test(collagen_Frank$zero_day_Compressed_Thickness ~ collagen_Frank$Total_solution_quantity, var.equal = FALSE)
compressed_t
```

##### The `r exp_date` data shows p-value is `r round(compressed_t$p.value,2)`  `r if(compressed_t$p.value > 0.05){" >= 0.05 which means we accept the H0 hypothesis."}else{"< 0.5 which means we reject the H0 hypothesis and accept the H1 hypothesis."}`

### 8. Reproducibility on the compressed thickness

```{r f test_compressed_reproducibility}
var.test(collagen_1ml$zero_day_Compressed_Thickness ~ collagen_1ml$Person)
```

```{r comparison_compressed_reproducibility}
reproducibility_compressed <- t.test(collagen_1ml$zero_day_Compressed_Thickness ~ collagen_1ml$Person, var.equal = TRUE)
reproducibility_compressed
```

##### The `r exp_date` data shows p-value is `r round(reproducibility_compressed$p.value,2)`  `r if(reproducibility_compressed$p.value > 0.05){" >= 0.05 which means we accept the H0 hypothesis."}else{"< 0.5 which means we reject the H0 hypothesis and accept the H1 hypothesis."}`

#### check the thickness difference between pH 7.7 and 9 buffer

```{r}
norph9 <- shapiro.test(collagen_Frank_1ml$UnCompressed_Thickness)
norph9
```


## Including Plots

### 1. the distribution of the `r exp_date` data
```{r normal plot, echo = FALSE}
simple.eda(collagen_Frank$UnCompressed_Thickness)
```

### 2. the comparison of the `r exp_date` data
```{r comparison, echo = FALSE}
barplotcomparison <- barplot(collagen_Frank_mean$UnCompressed_Thickness ~ collagen_Frank_mean$Group.1, ylim = c(0,800))
arrows(x0 = barplotcomparison,
       y1 = collagen_Frank_mean$UnCompressed_Thickness + collagen_Frank_sd$UnCompressed_Thickness,
       y0 = collagen_Frank_mean$UnCompressed_Thickness - collagen_Frank_sd$UnCompressed_Thickness,
       angle = 90,
       code = 3,
       length = 0.1
)
```

### 3. the comparison study on the `r exp_date` data with the prvious study
```{r reproducibility, echo = FALSE}
barplotreproducibility <- barplot(collagen_1ml_mean$UnCompressed_Thickness ~ collagen_1ml_mean$Group.1, ylim = c(0,750))
arrows(x0 = barplotreproducibility, 
       y0 = collagen_1ml_mean$UnCompressed_Thickness + collagen_1ml_sd$UnCompressed_Thickness,
       y1 = collagen_1ml_mean$UnCompressed_Thickness - collagen_1ml_sd$UnCompressed_Thickness,
       angle = 90,
       code = 3,
       length = 0.1
)
```

### 4. the distribution of the `r exp_date` data for Young's Modulus

```{r youngsdistribution, echo=FALSE}
simple.eda(collagen_Frank$Youngs_Modulus)
identify(collagen_Frank$Youngs_Modulus)
```

### 5. the comparison study on the `r exp_date` data for Young's Modulus

```{r youngs_plot, echo=FALSE}
barplotyoungs <- barplot(youngs_mean$Youngs_Modulus ~ youngs_mean$Group.1, ylim = c(0,3))
arrows(x0 = barplotcomparison,
       y1 = youngs_mean$Youngs_Modulus + youngs_sd$Youngs_Modulus,
       y0 = youngs_mean$Youngs_Modulus - youngs_sd$Youngs_Modulus,
       angle = 90,
       code = 3,
       length = 0.1
)
```

### 6. THe distribution of 1 ml collagen membrane in the `r exp_date` data after compressed

```{r normal plot 1ml compress, echo=FALSE}
simple.eda(collagen_Frank_1ml$zero_day_Compressed_Thickness)
```

### 7. The distribution of 1.5 ml collagen membrane in the `r exp_date` data after compressed

```{r normal plot 1.5ml compress, echo=FALSE}
simple.eda(collagen_Frank_1.5ml$zero_day_Compressed_Thickness)
```

### 8. The comparison of the compressed membrane bewteen different ammount

```{r comparision plot_compressed, echo=FALSE}
barplotcompress <- barplot(collagen_Frank_mean$zero_day_Compressed_Thickness ~ collagen_Frank_mean$Quantity, ylim = c(0,500))
arrows(x0 = barplotcomparison,
       y1 = collagen_Frank_mean$zero_day_Compressed_Thickness + collagen_Frank_sd$zero_day_Compressed_Thickness,
       y0 = collagen_Frank_mean$zero_day_Compressed_Thickness - collagen_Frank_sd$zero_day_Compressed_Thickness,
       angle = 90,
       code = 3,
       length = 0.1
)
```

```{r}
test <- ggbarplot(collagen_Frank_mean, x = "Quantity", y = "zero_day_Compressed_Thickness", 
          sort.by.groups = FALSE,     # Don't sort inside each group
          x.text.angle = 90           # Rotate vertically x axis texts
)
```


### 9. The reproducibility of the compressed membrane

```{r reproducibility plot_compressed, echo=FALSE}
barplotreproducibilitycompres <- barplot(collagen_1ml_mean$zero_day_Compressed_Thickness ~ collagen_1ml_mean$Group.1, ylim = c(0,500))
arrows(x0 = barplotreproducibility, 
       y0 = collagen_1ml_mean$zero_day_Compressed_Thickness + collagen_1ml_sd$zero_day_Compressed_Thickness,
       y1 = collagen_1ml_mean$zero_day_Compressed_Thickness - collagen_1ml_sd$zero_day_Compressed_Thickness,
       angle = 90,
       code = 3,
       length = 0.1
)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
