---
title: "Collagen Membrane on optimization"
author: "Frank"
date: "2022-09-25"
output:
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 1. Configure environment and include the data

The analysis is powered by `r version[['version.string']]`. It requires the following packages:

```{r libaray, message=FALSE}
library(readxl)
library(dplyr)
library(rstatix)
library(ggpubr)
library(ggplot2)
library(ggsignif)
library(ggeasy)
library(PMCMR)
library(PMCMRplus)
```

Read the data from the excel files

```{r excel, echo=FALSE}
collagen <- read_excel("E:/OneDrive/Tokyo Metropolitan University/Collagen Membrane/Collagen Membrane.xlsx", sheet = 2)
preparation <- read_excel("E:/OneDrive/Tokyo Metropolitan University/Collagen Membrane/Collagen Membrane.xlsx", sheet = 1)
collagen_compression <- merge(collagen,preparation,by="Group Name", all.x = TRUE)
head(collagen_compression,5)
```

```{r subgroup}
#ph7rpm3000centrifuge10 <- subset.data.frame(collagen_compression,`Buffer pH` == 7.7 & `Centrifuge (rpm)` == 3000 & `Centrifuge Time (min)` == 10)
#ph9rpm3000centrifuge10 <- subset.data.frame(collagen_compression,`Buffer pH` == 9 & `Centrifuge (rpm)` == 3000 & `Centrifuge Time (min)` == 10)
#ph7rpm3000centrifuge20 <- subset.data.frame(collagen_compression,`Buffer pH` == 7.7 & `Centrifuge (rpm)` == 3000 & `Centrifuge Time (min)` == 20)
#ph9rpm3000centrifuge20 <- subset.data.frame(collagen_compression,`Buffer pH` == 9 & `Centrifuge (rpm)` == 3000 & `Centrifuge Time (min)` == 20)
#ph7force500centrifuge10 <- subset.data.frame(collagen_compression,`Buffer pH` == 7.7 & `Centrifuge (rpm)` == 2116 & `Centrifuge Time (min)` == 10)
#ph9force500centrifuge10 <- subset.data.frame(collagen_compression,`Buffer pH` == 9 & `Centrifuge (rpm)` == 2116 & `Centrifuge Time (min)` == 10)
#ph7force500centrifuge20 <- subset.data.frame(collagen_compression,`Buffer pH` == 7.7 & `Centrifuge (rpm)` == 2116 & `Centrifuge Time (min)` == 20)
#ph9force500centrifuge20 <- subset.data.frame(collagen_compression,`Buffer pH` == 9 & `Centrifuge (rpm)` == 2116 & `Centrifuge Time (min)` == 20)
```

1.  Mean over the group

```{r}
meanAll <- aggregate.data.frame(collagen_compression[c("Thickness (μm)")],list(
  Group = collagen_compression$Group,
  Status = collagen_compression$Status, 
  pH = collagen_compression$`Buffer pH`, 
  Quantity = collagen_compression$`Total solution quantity (ml)`, 
  Centrifuge = collagen_compression$`Centrifuge (rpm)`, 
  CentrifugeTime =collagen_compression$`Centrifuge Time (min)`),mean)
meanAll
```

## Synthesis Matrix of the Compression Ratio

```{r}
Data <- subset.data.frame(collagen_compression,`Status` != "Uncompressed" & "Centrifuge Time (min)" != 5 & `Centrifuge (rpm)` == 3000 & `Centrifuge Time (min)` == 10 & `Person`=="Frank") %>%
  group_by(across(all_of(c("Group Name","Status","Buffer pH","Total solution quantity (ml)","Centrifuge (rpm)","Centrifuge Time (min)")))) %>%
  summarise(
    count = n(),
    mean = round(mean(`Compressed Ratio`, na.rm = TRUE),3),
    sd = sd(`Compressed Ratio`, na.rm = TRUE),
    median = median(`Compressed Ratio`, na.rm = TRUE),
    IQR = IQR(`Compressed Ratio`, na.rm = TRUE)
  )
Data
```

2.  SD over the group

```{r}
sdAll <- aggregate.data.frame(collagen_compression[c("Thickness (μm)")],list(
  Group = collagen_compression$Group,
  Status = collagen_compression$Status, 
  pH = collagen_compression$`Buffer pH`, 
  Quantity = collagen_compression$`Total solution quantity (ml)`, 
  Centrifuge = collagen_compression$`Centrifuge (rpm)`, 
  CentrifugeTime =collagen_compression$`Centrifuge Time (min)`),sd)
sdAll
```

3.  Merge mean and sd

```{r}
meansd <- merge(meanAll,sdAll,by="Group")
meansd <- rename(meansd,c("mean"="Thickness (μm).x","SD"="Thickness (μm).y"))
meansd
```

4.  Observe the compression ratio

    ```{r}
    collagen_compression_ratio <- subset.data.frame(collagen_compression,Status != "Uncompressed" & Person != "Oyamasan")
    CompressedRatio <- aggregate.data.frame(
      collagen_compression_ratio[c("Compressed Ratio")],
      list(
        Person = collagen_compression_ratio$Person,
        Group = collagen_compression_ratio$Group,
        Status = collagen_compression_ratio$Status, 
        pH = collagen_compression_ratio$`Buffer pH`, 
        Quantity = collagen_compression_ratio$`Total solution quantity (ml)`, 
        Centrifuge = collagen_compression_ratio$`Centrifuge (rpm)`, 
        CentrifugeTime = collagen_compression_ratio$`Centrifuge Time (min)`),
      mean)
    CompressedRatio
    ```

5.  Examine the distribution of compression ration

    ```{r}
    shapiro.test(subset.data.frame(CompressedRatio,Status=="Compressed")$`Compressed Ratio`)
    ```

6.  The plot of the compressed

    ```{r}
    ggplot(subset.data.frame(CompressedRatio,Status=="Compressed"), aes(x=Quantity, y=`Compressed Ratio`))+ 
      geom_jitter(position=position_jitter(0.2), cex=1.2) + 
      stat_summary(fun.y=mean, geom="point", shape=18, size=3, color="red")
    ```

7.  Buffer pH 7.7, 2116 rpm (500 g force), and 20 mins centrifuge times

    ```{r}
    aggregate.data.frame(
      ph7force500centrifuge20[c("Thickness (μm)")],
      list(Operator = ph7force500centrifuge20$Person,
           Status = ph7force500centrifuge20$Status,
           Quantity = ph7force500centrifuge20$`Total solution quantity (ml)`),
      mean)
    ```

8.  Buffer pH 9, 2116 rpm (500 g force), and 20 mins centrifuge times

    ```{r}
    aggregate.data.frame(
      ph9force500centrifuge20[c("Thickness (μm)")],
      list(Operator = ph9force500centrifuge20$Person,
           Status = ph9force500centrifuge20$Status,
           Quantity = ph9force500centrifuge20$`Total solution quantity (ml)`),
      mean)
    ```

## 2. One-way ANOVA test

```{r ano}
colmembrane <- aov(`Thickness (μm)` ~ Group, data = subset.data.frame(collagen_compression, Person == "Frank"))
summary(colmembrane)
```

```{r}
tukeycolmembrane <- tukey_hsd(colmembrane)
tukeycolmembrane
selected <- subset.data.frame(tukeycolmembrane,p.adj.signif != "ns")
selected
```

```{r}
#ggboxplot(collagen_compression, x = "Group", y= "Thickness (μm)", color="Status", add = "jitter", xlab = "Test Date")
ggbarplot(meansd, x = "Group", y= "mean", fill = "Status")+ 
   geom_bar(stat="identity", position=position_dodge())+
   geom_errorbar(aes(ymin=mean-SD, ymax=mean+SD), width=.2,
                 position=position_dodge(.9))+
   stat_pvalue_manual(
     selected,
     label = "p.adj.signif",
     y.position = seq(from=900, to=1809, by=10)
   )
```

## Examine the Centrifuge 3000 rpm, 10 min at different pH buffer and quantity

```{r}
centrifuge3000rpm10min <- subset.data.frame(collagen_compression, `Centrifuge (rpm)` == 3000 & `Centrifuge Time (min)` == 10 & Person == "Frank")
colnames(centrifuge3000rpm10min)[which(names(centrifuge3000rpm10min)=="Buffer pH")] <- "pH"
colnames(centrifuge3000rpm10min)[which(names(centrifuge3000rpm10min)== "Total solution quantity (ml)")] <- "Quantity"
colnames(centrifuge3000rpm10min)[which(names(centrifuge3000rpm10min)== "Compressed Ratio")] <- "Ratio"
colnames(centrifuge3000rpm10min)[which(names(centrifuge3000rpm10min)== "Centrifuge (rpm)")] <- "Centrifuge"
colnames(centrifuge3000rpm10min)[which(names(centrifuge3000rpm10min)== "Centrifuge Time (min)")] <- "CentrifugeTime"
colnames(centrifuge3000rpm10min)[which(names(centrifuge3000rpm10min)== "Group Name")] <- "Condition"
head(centrifuge3000rpm10min,5)
```

check the normality

```{r}
shapiro.test(subset.data.frame(centrifuge3000rpm10min,`pH` == 7.7 & `Quantity` == 1 & `Status` == "Compressed")$`Ratio`)
shapiro.test(subset.data.frame(centrifuge3000rpm10min,`pH` == 7.7 & `Quantity` == 1 & `Status` == "After7DaysCompressed")$`Ratio`)
shapiro.test(subset.data.frame(centrifuge3000rpm10min,`pH` == 7.7 & `Quantity` == 1.5 & `Status` == "Compressed")$`Ratio`)
shapiro.test(subset.data.frame(centrifuge3000rpm10min,`pH` == 7.7 & `Quantity` == 1.5 & `Status` == "After7DaysCompressed")$`Ratio`)
shapiro.test(subset.data.frame(centrifuge3000rpm10min,`pH` == 9 & `Quantity` == 1 & `Status` == "Compressed")$`Ratio`)
shapiro.test(subset.data.frame(centrifuge3000rpm10min,`pH` == 9 & `Quantity` == 1 & `Status` == "After7DaysCompressed")$`Ratio`)
shapiro.test(subset.data.frame(centrifuge3000rpm10min,`pH` == 9 & `Quantity` == 1.5 & `Status` == "Compressed")$`Ratio`)
shapiro.test(subset.data.frame(centrifuge3000rpm10min,`pH` == 9 & `Quantity` == 1.5 & `Status` == "After7DaysCompressed")$`Ratio`)
```

Examine the comparison study

```{r}
pstat <- compare_means(`Ratio` ~ `Group`, data = centrifuge3000rpm10min, method = "kruskal.test")
pstat
```

```{r}
dun <- centrifuge3000rpm10min %>%
  group_by(Quantity,pH) %>%
  dunn_test(Ratio ~ Status) %>%
  add_xy_position(x="Status", fun = "mean_sd", dodge = 0.8)
dun
```

```{r}
ggbarplot(Data, x = "Status", y= "mean", fill ="Status", ylab = "Compression Ratio", lab.size = 3,lab.pos = "in", order = c("Compressed","After7DaysCompressed"))+
  facet_grid(Data$'pH' ~ Data$'Quantity', scales = "free")+ 
   geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.2,
               position=position_dodge(.9))
#ggplot(Data, aes(fill=`Status`, y=`mean`, x=`Buffer pH`)) + 
   # geom_bar(position="dodge", stat="identity")
```

```{r}
centrifuge3000rpm10min$pH <- as.factor(centrifuge3000rpm10min$pH)
ggline(centrifuge3000rpm10min, x = "Status", y= "Ratio",add = c("mean_se", "jitter",ylab = "Compression Ratio"), fill ="pH", color = "pH", facet.by = "Quantity", order = c("Compressed","After7DaysCompressed"), panel.labs = list(Quantity = c("1 ml collagen","1.5 ml collage")), ylab = c("Compression Ratio"))+
  ggtitle("Centrifuge at 3000 rpm (1000 g) for 10 mins") +
  easy_center_title()+
  stat_pvalue_manual(dun, hide.ns = TRUE)+
  scale_y_continuous(expand = expansion(mult = c(0.05, 0.15)))
```

## Examine the Centrifuge 3000 rpm, 20 min at different pH buffer and quantity

```{r}
centrifuge3000rpm20min <- subset.data.frame(collagen_compression, `Centrifuge (rpm)` == 3000 & `Centrifuge Time (min)` == 20 & Person == "Frank" & `Status` != "Uncompressed")
colnames(centrifuge3000rpm20min)[which(names(centrifuge3000rpm20min)=="Buffer pH")] <- "pH"
colnames(centrifuge3000rpm20min)[which(names(centrifuge3000rpm20min)== "Total solution quantity (ml)")] <- "Quantity"
colnames(centrifuge3000rpm20min)[which(names(centrifuge3000rpm20min)== "Compressed Ratio")] <- "Ratio"
colnames(centrifuge3000rpm20min)[which(names(centrifuge3000rpm20min)== "Centrifuge (rpm)")] <- "Centrifuge"
colnames(centrifuge3000rpm20min)[which(names(centrifuge3000rpm20min)== "Centrifuge Time (min)")] <- "CentrifugeTime"
colnames(centrifuge3000rpm20min)[which(names(centrifuge3000rpm20min)== "Group Name")] <- "Condition"
head(centrifuge3000rpm20min,5)
```

```{r}
Data <- centrifuge3000rpm20min %>%
  group_by(across(all_of(c("Condition","Status","pH","Quantity","Centrifuge","CentrifugeTime","Group")))) %>%
  summarise(
    count = n(),
    mean = round(mean(`Ratio`, na.rm = TRUE),3),
    sd = sd(`Ratio`, na.rm = TRUE),
    median = median(`Ratio`, na.rm = TRUE),
    IQR = IQR(`Ratio`, na.rm = TRUE)
  )
Data
```

```{r}
shapiro.test(subset.data.frame(centrifuge3000rpm20min,`Buffer pH` == 7.7 & `Total solution quantity (ml)` == 1 & `Status` == "Compressed")$`Compressed Ratio`)
shapiro.test(subset.data.frame(centrifuge3000rpm20min,`Buffer pH` == 7.7 & `Total solution quantity (ml)` == 1 & `Status` == "After7DaysCompressed")$`Compressed Ratio`)
shapiro.test(subset.data.frame(centrifuge3000rpm20min,`Buffer pH` == 7.7 & `Total solution quantity (ml)` == 1.5 & `Status` == "Compressed")$`Compressed Ratio`)
shapiro.test(subset.data.frame(centrifuge3000rpm20min,`Buffer pH` == 7.7 & `Total solution quantity (ml)` == 1.5 & `Status` == "After7DaysCompressed")$`Compressed Ratio`)
shapiro.test(subset.data.frame(centrifuge3000rpm20min,`Buffer pH` == 9 & `Total solution quantity (ml)` == 1 & `Status` == "Compressed")$`Compressed Ratio`)
shapiro.test(subset.data.frame(centrifuge3000rpm20min,`Buffer pH` == 9 & `Total solution quantity (ml)` == 1 & `Status` == "After7DaysCompressed")$`Compressed Ratio`)
shapiro.test(subset.data.frame(centrifuge3000rpm20min,`Buffer pH` == 9 & `Total solution quantity (ml)` == 1.5 & `Status` == "Compressed")$`Compressed Ratio`)
shapiro.test(subset.data.frame(centrifuge3000rpm20min,`Buffer pH` == 9 & `Total solution quantity (ml)` == 1.5 & `Status` == "After7DaysCompressed")$`Compressed Ratio`)
```

```{r}
pstat <- compare_means(`Ratio` ~ `Group`, data = centrifuge3000rpm20min, method = "kruskal.test")
pstat
```

```{r}
#dun <- dunn_test(centrifuge3000rpm20min,`Ratio` ~ `Group`)
#dun
dun <- centrifuge3000rpm20min %>%
  group_by(Quantity,pH) %>%
  dunn_test(Ratio ~ Status) %>%
  add_xy_position(x="Status", fun = "mean_sd", dodge = 0.8)
dun
```

```{r}
ggbarplot(Data, x = "Status", y= "mean", fill ="Status", ylab = "Compression Ratio", lab.size = 3,label = TRUE,lab.pos = "in", order = c("Compressed","After7DaysCompressed"))+
  facet_grid(Data$'pH' ~ Data$'Quantity')+
   geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.2,
               position=position_dodge(.9))
```

```{r}
centrifuge3000rpm20min$pH <- as.factor(centrifuge3000rpm20min$pH)
ggline(centrifuge3000rpm20min, x = "Status", y= "Ratio",add = c("mean_se", "jitter"), fill ="pH", color = "pH", facet.by = "Quantity", order = c("Compressed","After7DaysCompressed"), panel.labs = list(Quantity = c("1 ml collagen","1.5 ml collage")), ylab = c("Compression Ratio"))+
  ggtitle("Centrifuge at 3000 rpm (1000 g) for 20 mins") +
  easy_center_title()+
  stat_pvalue_manual(dun, hide.ns = TRUE)+
  scale_y_continuous(expand = expansion(mult = c(0.05, 0.15)))
```

## Examine the Centrifuge 2116 rpm, 10 min at different pH buffer and quantity

```{r}
centrifuge2116rpm10min <- subset.data.frame(collagen_compression, `Centrifuge (rpm)` == 2116 & `Centrifuge Time (min)` == 10 & Person == "Frank" & `Status` != "Uncompressed")
colnames(centrifuge2116rpm10min)[which(names(centrifuge2116rpm10min)=="Buffer pH")] <- "pH"
colnames(centrifuge2116rpm10min)[which(names(centrifuge2116rpm10min)== "Total solution quantity (ml)")] <- "Quantity"
colnames(centrifuge2116rpm10min)[which(names(centrifuge2116rpm10min)== "Compressed Ratio")] <- "Ratio"
colnames(centrifuge2116rpm10min)[which(names(centrifuge2116rpm10min)== "Centrifuge (rpm)")] <- "Centrifuge"
colnames(centrifuge2116rpm10min)[which(names(centrifuge2116rpm10min)== "Centrifuge Time (min)")] <- "CentrifugeTime"
colnames(centrifuge2116rpm10min)[which(names(centrifuge2116rpm10min)== "Group Name")] <- "Condition"
head(centrifuge2116rpm10min,5)
```

```{r}
Data <- centrifuge2116rpm10min %>%
  group_by(across(all_of(c("Condition","Status","pH","Quantity","Centrifuge","CentrifugeTime")))) %>%
  summarise(
    count = n(),
    mean = round(mean(`Ratio`, na.rm = TRUE),3),
    sd = sd(`Ratio`, na.rm = TRUE),
    median = median(`Ratio`, na.rm = TRUE),
    IQR = IQR(`Ratio`, na.rm = TRUE)
  )
Data
```

```{r}
shapiro.test(subset.data.frame(centrifuge2116rpm10min,`pH` == 7.7 & `Quantity` == 1 & `Status` == "Compressed")$`Ratio`)
shapiro.test(subset.data.frame(centrifuge2116rpm10min,`pH` == 7.7 & `Quantity` == 1 & `Status` == "After7DaysCompressed")$`Ratio`)
shapiro.test(subset.data.frame(centrifuge2116rpm10min,`pH` == 7.7 & `Quantity` == 1.5 & `Status` == "Compressed")$`Ratio`)
shapiro.test(subset.data.frame(centrifuge2116rpm10min,`pH` == 7.7 & `Quantity` == 1.5 & `Status` == "After7DaysCompressed")$`Ratio`)
shapiro.test(subset.data.frame(centrifuge2116rpm10min,`pH` == 9 & `Quantity` == 1 & `Status` == "Compressed")$`Ratio`)
shapiro.test(subset.data.frame(centrifuge2116rpm10min,`pH` == 9 & `Quantity` == 1 & `Status` == "After7DaysCompressed")$`Ratio`)
shapiro.test(subset.data.frame(centrifuge2116rpm10min,`pH` == 9 & `Quantity` == 1.5 & `Status` == "Compressed")$`Ratio`)
shapiro.test(subset.data.frame(centrifuge2116rpm10min,`pH` == 9 & `Quantity` == 1.5 & `Status` == "After7DaysCompressed")$`Ratio`)
```

```{r}
pstat <- compare_means(`Ratio` ~ `Group`, data = centrifuge2116rpm10min, method = "kruskal.test")
pstat
```

```{r}
#dunn_test(centrifuge2116rpm10min,`Ratio` ~ `Group`)
dun <- centrifuge2116rpm10min %>%
  group_by(Quantity,pH) %>%
  dunn_test(Ratio ~ Status) %>%
  add_xy_position(x="Status", fun = "mean_sd", dodge = 0.8)
dun
```

```{r}
ggbarplot(Data, x = "Status", y= "mean", fill ="Status", ylab = "Compression Ratio", lab.size = 3,label = TRUE,lab.pos = "in", order = c("Compressed","After7DaysCompressed"))+
  facet_grid(Data$'pH' ~ Data$'Quantity')+ 
   geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.2,
               position=position_dodge(.9))
```

```{r}
centrifuge2116rpm10min$pH <- as.factor(centrifuge2116rpm10min$pH)
ggline(centrifuge2116rpm10min, x = "Status", y= "Ratio",add = c("mean_se", "jitter"), fill ="pH", color = "pH", facet.by = "Quantity", order = c("Compressed","After7DaysCompressed"), panel.labs = list(Quantity = c("1 ml collagen","1.5 ml collage")), ylab = c("Compression Ratio"))+
  ggtitle("Centrifuge at 2116 rpm (500 g) for 10 mins") +
  easy_center_title()+
  stat_pvalue_manual(dun, hide.ns = TRUE)+
  scale_y_continuous(expand = expansion(mult = c(0.05, 0.15)))
```

## Examine the Centrifuge 2116 rpm, 20 min at different pH buffer and quantity

```{r}
centrifuge2116rpm20min <- subset.data.frame(collagen_compression, `Centrifuge (rpm)` == 2116 & `Centrifuge Time (min)` == 20 & Person == "Frank" & `Status` != "Uncompressed")
colnames(centrifuge2116rpm20min)[which(names(centrifuge2116rpm20min)=="Buffer pH")] <- "pH"
colnames(centrifuge2116rpm20min)[which(names(centrifuge2116rpm20min)== "Total solution quantity (ml)")] <- "Quantity"
colnames(centrifuge2116rpm20min)[which(names(centrifuge2116rpm20min)== "Compressed Ratio")] <- "Ratio"
colnames(centrifuge2116rpm20min)[which(names(centrifuge2116rpm20min)== "Centrifuge (rpm)")] <- "Centrifuge"
colnames(centrifuge2116rpm20min)[which(names(centrifuge2116rpm20min)== "Centrifuge Time (min)")] <- "CentrifugeTime"
colnames(centrifuge2116rpm20min)[which(names(centrifuge2116rpm20min)== "Group Name")] <- "Condition"
head(centrifuge2116rpm20min,5)
```

```{r}
Data <- centrifuge2116rpm20min %>%
  group_by(across(all_of(c("Condition","Status","pH","Quantity","Centrifuge","CentrifugeTime","Group")))) %>%
  summarise(
    count = n(),
    mean = round(mean(`Ratio`, na.rm = TRUE),3),
    sd = sd(`Ratio`, na.rm = TRUE),
    median = median(`Ratio`, na.rm = TRUE),
    IQR = IQR(`Ratio`, na.rm = TRUE)
  )
Data
```

```{r}
shapiro.test(subset.data.frame(centrifuge2116rpm20min,`pH` == 7.7 & `Quantity` == 1 & `Status` == "Compressed")$`Ratio`)
shapiro.test(subset.data.frame(centrifuge2116rpm20min,`pH` == 7.7 & `Quantity` == 1 & `Status` == "After7DaysCompressed")$`Ratio`)
shapiro.test(subset.data.frame(centrifuge2116rpm20min,`pH` == 7.7 & `Quantity` == 1.5 & `Status` == "Compressed")$`Ratio`)
shapiro.test(subset.data.frame(centrifuge2116rpm20min,`pH` == 7.7 & `Quantity` == 1.5 & `Status` == "After7DaysCompressed")$`Ratio`)
shapiro.test(subset.data.frame(centrifuge2116rpm20min,`pH` == 9 & `Quantity` == 1 & `Status` == "Compressed")$`Ratio`)
shapiro.test(subset.data.frame(centrifuge2116rpm20min,`pH` == 9 & `Quantity` == 1 & `Status` == "After7DaysCompressed")$`Ratio`)
shapiro.test(subset.data.frame(centrifuge2116rpm20min,`pH` == 9 & `Quantity` == 1.5 & `Status` == "Compressed")$`Ratio`)
shapiro.test(subset.data.frame(centrifuge2116rpm20min,`pH` == 9 & `Quantity` == 1.5 & `Status` == "After7DaysCompressed")$`Ratio`)
```

```{r}
pstat <- compare_means(`Ratio` ~ `Group`, data = centrifuge2116rpm20min, method = "kruskal.test")
pstat
```

```{r}
#dun <- dunn_test(centrifuge2116rpm20min,`Ratio` ~ `Group`)
#dun
dun <- centrifuge2116rpm20min %>%
  group_by(Quantity,pH) %>%
  dunn_test(Ratio ~ Status) %>%
  add_xy_position(x="Status", fun = "mean_sd", dodge = 0.8)
dun
posthoc.f
```

```{r}
ggbarplot(Data, x = "Group", y= "mean", fill ="Status", ylab = "Compression Ratio", lab.size = 3,label = TRUE,lab.pos = "in", order = c("Compressed","After7DaysCompressed"))+
  facet_grid(Data$'pH' ~ Data$'Quantity')+ 
   geom_errorbar(aes(ymin=mean-sd, ymax=mean+sd), width=.2,
               position=position_dodge(.9))

```

```{r}
centrifuge2116rpm20min$pH <- as.factor(centrifuge2116rpm20min$pH)
ggline(centrifuge2116rpm20min, x = "Status", y= "Ratio",add = c("mean_se", "jitter"), color = "pH", facet.by = "Quantity", panel.labs = list(Quantity = c("1 ml collagen","1.5 ml collage")), ylab = c("Compression Ratio"))+
  ggtitle("Centrifuge at 2116 rpm (500 g) for 20 mins") +
  easy_center_title()+
  stat_pvalue_manual(dun, hide.ns = TRUE)+
  scale_y_continuous(expand = expansion(mult = c(0.05, 0.15)))
```

## Compared the compression

```{r}
Data <- subset.data.frame(collagen_compression,`Status` == "Compressed" & "Centrifuge Time (min)" != 5 & `Person`=="Frank") %>%
  group_by(across(all_of(c("Group Name","Status","Buffer pH","Total solution quantity (ml)","Centrifuge (rpm)","Centrifuge Time (min)")))) %>%
  summarise(
    count = n(),
    mean = round(mean(`Compressed Ratio`, na.rm = TRUE),3),
    sd = sd(`Compressed Ratio`, na.rm = TRUE),
    median = median(`Compressed Ratio`, na.rm = TRUE),
    IQR = IQR(`Compressed Ratio`, na.rm = TRUE)
  )
Data
colnames(Data)[which(names(Data)=="Buffer pH")] <- "pH"
colnames(Data)[which(names(Data)== "Total solution quantity (ml)")] <- "Quantity"
colnames(Data)[which(names(Data)== "Compressed Ratio")] <- "Ratio"
colnames(centrifuge3000rpm10min)[which(names(centrifuge3000rpm10min)== "Centrifuge (rpm)")] <- "Centrifuge"
colnames(centrifuge3000rpm10min)[which(names(centrifuge3000rpm10min)== "Centrifuge Time (min)")] <- "CentrifugeTime"
colnames(centrifuge3000rpm10min)[which(names(centrifuge3000rpm10min)== "Group Name")] <- "Condition"
```

```{r}
Data %>%
  group_by()
```

## 3. Young's Modulus

## To find out the prediction model

```{r}
youngs <- subset.data.frame(collagen_compression, Person == "Frank")
colnames(youngs)[which(names(youngs)=="Buffer pH")] <- "pH"
colnames(youngs)[which(names(youngs)== "Total solution quantity (ml)")] <- "Quantity"
colnames(youngs)[which(names(youngs)== "Compressed Ratio")] <- "Ratio"
colnames(youngs)[which(names(youngs)== "Centrifuge (rpm)")] <- "Centrifuge"
colnames(youngs)[which(names(youngs)== "Centrifuge Time (min)")] <- "CentrifugeTime"
colnames(youngs)[which(names(youngs)== "Group Name")] <- "Condition"
colnames(youngs)[which(names(youngs)== "Youngs Modulus (kPa)")] <- "Youngs_Modulus"
head(youngs,5)
```

```{r}
Data <- youngs %>%
  group_by(across(all_of(c("Area","Date.x")))) %>%
  summarise(
    count = n(),
    mean = round(mean(`Youngs_Modulus`, na.rm = TRUE),3),
    sd = sd(`Youngs_Modulus`, na.rm = TRUE),
    median = median(`Youngs_Modulus`, na.rm = TRUE),
    IQR = IQR(`Youngs_Modulus`, na.rm = TRUE)
  )
Data
```

```{r}
shapiro.test(subset.data.frame(youngs, Area == "Highest")$Youngs_Modulus)
shapiro.test(subset.data.frame(youngs, Area == "Middle")$Youngs_Modulus)
shapiro.test(subset.data.frame(youngs, Area == "Low")$Youngs_Modulus)
```

```{r}
youngtest <- aov(Youngs_Modulus ~ Area, subset.data.frame(youngs, Date.x >= as.Date('2022-10-20')))
summary(youngtest)
```

```{r}
pstat <- compare_means(Youngs_Modulus ~ Area , data = youngs, method = "kruskal.test")
pstat
```

```{r}
dun <- youngs %>%
  dunn_test(Youngs_Modulus ~ Area) %>%
  add_xy_position(x="Status", fun = "mean_sd", dodge = 0.8)
dun
```

```{r}
var.test(Youngs_Modulus ~ Quantity, subset.data.frame(youngs, pH == 7.7 & Status == "Compressed"))
```

```{r}
t.test(Youngs_Modulus ~ Quantity, subset.data.frame(youngs, pH == 7.7 & Status == "Compressed"))
```
