---
title: "Day1_inverseAspectRatio"
author: "Frank"
date: "2022-09-22"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Configuration

The analysis is powered by `r version[['version.string']]`. It requires the following packages:

```{r library, message=FALSE}
library(readxl)
library(UsingR)
library(ggpubr)
library(ggplot2)
library(ggsignif)
library(dplyr)
library(ggeasy)
library(ggplot2)
library(rstatix)
library(PMCMRplus)
```

## Reading the Raw Data From Excel

```{r excel, echo=FALSE}
inverseAspectRatio <- read_xlsx("F:/M2/でーたまとめ/statistic.xlsx",sheet = 1)
inverseAspectRatio
```

 ## Table on the Data

```{r, echo=FALSE}
#aggregate(inverseAspectRatio[c("nomarized inverce aspect ratio")],list(group=inverseAspectRatio$`SC or CS`),mean)
SynthesisMatrix <- inverseAspectRatio %>%
  group_by(`Stretch`,`Speed`,`Time`,`GroupName`) %>%
  summarise(
    count = n(),
    mean = mean(`Strain`, na.rm = TRUE),
    sd = sd(`Strain`, na.rm = TRUE),
    median = median(`Strain`, na.rm = TRUE),
    IQR = IQR(`Strain`, na.rm = TRUE),
    se = sd(`Strain`, na.rm = TRUE)/sqrt(n())
  )
SynthesisMatrix
```

```{r divide the group, echo=FALSE, include=FALSE}
F1 <- subset.data.frame(inverseAspectRatio,inverseAspectRatio$`GroupName`=="5s2.5%0.005s")
F2 <- subset.data.frame(inverseAspectRatio,inverseAspectRatio$`GroupName`=="1s2.5%0.025s")
F3 <- subset.data.frame(inverseAspectRatio,inverseAspectRatio$`GroupName`=="8s4%0.005s")
F4<- subset.data.frame(inverseAspectRatio,inverseAspectRatio$`GroupName`=="1.6s4%0.025s")
F5<- subset.data.frame(inverseAspectRatio,inverseAspectRatio$`GroupName`=="10s5%0.005s")
F6<- subset.data.frame(inverseAspectRatio,inverseAspectRatio$`GroupName`=="11s5%0.005s")
F7<- subset.data.frame(inverseAspectRatio,inverseAspectRatio$`GroupName`=="2s5%0.025s")
F8<- subset.data.frame(inverseAspectRatio,inverseAspectRatio$`GroupName`=="3s5%0.025s")
```

Check the normality and decide to run Student T-test or Wilcox Rank Sum test (U test).

```{r check normality, echo=FALSE}
normalTest <- shapiro.test(F1$`Strain`)
simple.eda(F1$`Strain`)
normalTest
```

```{r, echo=FALSE}
normalTest_F2 <- shapiro.test(F2$`Strain`)
simple.eda(F2$`Strain`)
normalTest_F2
```

```{r}
normalTest_F3 <- shapiro.test(F3$`Strain`)
simple.eda(F3$`Strain`)
normalTest_F3
```

```{r}
normalTest_F4 <- shapiro.test(F4$`Strain`)
simple.eda(F4$`Strain`)
normalTest_F4
```
```{r}
normalTest_F5 <- shapiro.test(F5$`Strain`)
simple.eda(F5$`Strain`)
normalTest_F5
```
```{r}
normalTest_F6 <- shapiro.test(F6$`Strain`)
simple.eda(F6$`Strain`)
normalTest_F6
```
```{r}
normalTest_F7 <- shapiro.test(F7$`Strain`)
simple.eda(F7$`Strain`)
normalTest_F7
```
```{r}
normalTest_F8 <- shapiro.test(F8$`Strain`)
simple.eda(F8$`Strain`)
normalTest_F8
```


## Run comparison

```{r U-test, echo=FALSE}
pstat <- compare_means(`Strain` ~ `GroupName`,data = inverseAspectRatio, method = "kruskal.test")
pstat
```

## Run post-hoc

```{r}
dun <- inverseAspectRatio %>%
  dunn_test(`Strain` ~ `GroupName`, p.adjust.method="bonferroni") %>%
  add_xy_position(x="GroupName", fun = "mean_sd", dodge = 0.8)
dun
```


## The plot

```{r}
ggbarplot(SynthesisMatrix, x="GroupName", y="mean", ylab = "Strain")+ 
  geom_bar(stat="identity", position=position_dodge())+
  geom_errorbar(aes(ymin=mean-se, ymax=mean+se), width=.2, position=position_dodge(.9))+
  stat_pvalue_manual(dun, hide.ns = TRUE)+
  ggtitle("Strech Strain XX on Nucleus")+
  easy_center_title()+ 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
```


```{r}
var.test(F5$Strain,F6$Strain)
t.test(F5$Strain,F6$Strain,  var.equal = TRUE)
```

```{r}
var.test(F1$Strain,F2$Strain)
t.test(F1$Strain,F2$Strain,  var.equal = TRUE)
```
```{r}
var.test(F3$Strain,F4$Strain)
t.test(F3$Strain,F4$Strain,  var.equal = TRUE)
```

```{r}
var.test(F7$Strain,F8$Strain)
t.test(F7$Strain,F8$Strain,  var.equal = TRUE)
```

## Read equivalent stretch Excel

```{r}
inverseAspectRatio <- read_xlsx("F:/M2/でーたまとめ/statistic.xlsx",sheet = 2)
inverseAspectRatio
```
### Create a seperated data sheet

```{r}
F1 <- subset.data.frame(inverseAspectRatio,inverseAspectRatio$`GroupName`=="5s2.5%0.005s")
F2 <- subset.data.frame(inverseAspectRatio,inverseAspectRatio$`GroupName`=="1s2.5%0.025s")
F3 <- subset.data.frame(inverseAspectRatio,inverseAspectRatio$`GroupName`=="8s4%0.005s")
F4<- subset.data.frame(inverseAspectRatio,inverseAspectRatio$`GroupName`=="1.6s4%0.025s")
F5<- subset.data.frame(inverseAspectRatio,inverseAspectRatio$`GroupName`=="10s5%0.005s")
F6<- subset.data.frame(inverseAspectRatio,inverseAspectRatio$`GroupName`=="11s5%0.005s")
F7<- subset.data.frame(inverseAspectRatio,inverseAspectRatio$`GroupName`=="2s5%0.025s")
F8<- subset.data.frame(inverseAspectRatio,inverseAspectRatio$`GroupName`=="3s5%0.025s")
```


### Equivalent Strain matrix

```{r}
SynthesisMatrix <- inverseAspectRatio %>%
  group_by(`Stretch`,`Speed`,`Time`,`GroupName`) %>%
  summarise(
    count = n(),
    mean = mean(`Strain`, na.rm = TRUE),
    sd = sd(`Strain`, na.rm = TRUE),
    median = median(`Strain`, na.rm = TRUE),
    IQR = IQR(`Strain`, na.rm = TRUE),
    se = sd(`Strain`, na.rm = TRUE)/sqrt(n())
  )
SynthesisMatrix
```

### Equivalent strain comparison

```{r U-test, echo=FALSE}
pstat <- compare_means(`Strain` ~ `GroupName`,data = inverseAspectRatio, method = "kruskal.test")
pstat
```


```{r}
dun <- inverseAspectRatio %>%
  dunn_test(`Strain` ~ `GroupName`, p.adjust.method="bonferroni") %>%
  add_xy_position(x="GroupName", fun = "mean_sd", dodge = 0.8)
dun
```
```{r}
ggbarplot(SynthesisMatrix, x="GroupName", y="mean", ylab = "Strain")+ 
  geom_bar(stat="identity", position=position_dodge())+
  geom_errorbar(aes(ymin=mean-se, ymax=mean+se), width=.2, position=position_dodge(.9))+
  stat_pvalue_manual(dun, hide.ns = TRUE)+
  ggtitle("Strech Strain XX on Nucleus")+
  easy_center_title()+ 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
```

```{r}
var.test(F1$Strain,F2$Strain)
t.test(F1$Strain,F2$Strain,  var.equal = FALSE)
```
```{r}
var.test(F3$Strain,F4$Strain)
t.test(F3$Strain,F4$Strain,  var.equal = TRUE)
```

```{r}
var.test(F5$Strain,F6$Strain)
t.test(F5$Strain,F6$Strain,  var.equal = TRUE)
```

```{r}
var.test(F7$Strain,F8$Strain)
t.test(F7$Strain,F8$Strain,  var.equal = TRUE)
```

