---
title: "1st Homework of 2019 TMU Biostatistics"
author: Bo-Jiang Lin
date: 2019-8-15
output: html_document
---

```{r, include=FALSE, echo = FALSE}
library(formattable)
```

##### 1. The demography table contains the smoke-related cancer population of Z city. The research is to delineate the relation between smoke and lung cancer.

1. What is the probability of a person with smoking if we pick up randomly?
```{r, echo=FALSE}
percent(2000 / 10000)
```
2. What is the probability of a healthy person with smoking if we pick up randomly?

```{r, echo=FALSE}
percent(1980/2000)
```
3. What is the probability of a patient if we randomly pick him up from the smoking group?

```{r, echo=FALSE}
percent(20/10000)
```
##### 2. A mouse has a 20% chance of lung cancer if second-hand smoke exposed to it last month. The research is designed on the 30 mice under the exposure of second-hand smoke.
1. What is the probability of 3 mice with lung cancer after one month?

```{r, echo=FALSE}
percent(choose(30,3)*(0.2 ^ 3) * (0.8 ^ 27))
```
2. What is the mean and variance of the number of mice with lung cancer after one month?

```{r}
mean <- (30 * 0.2)
variance <- (30 * 0.2 * 0.8)
lungcancer <- c(mean, variance)
names(lungcancer) <- c("mean", "variance")
formattable(lungcancer)
```
3. What is the probability of more than 8 mice with lung cancer after one month? using C.I.T.

```{r}
lungcancer8 <- c(0)
for (i in c(1:8)) {
    lungcancer8 <- lungcancer8 + choose(30, i) * (0.2 ^ i) * (0.8 ^ (30 - i))
}
percent(1 - lungcancer8)
```
##### 3. The chance of the car accident on the cross-road is poisson distribution. The lambda is 1.5 accidents per year.¦¸¡C
1. What is the probability of two accidents in one year?

```{r}
percent(ppois(2,lambda = 1.5))
```

2. Give from the same odd (lambda = 1.5) of the dependent car accident, what is the mean and variance in the successive three years?

```{r, echo=FALSE}
1.5+1.5+1.5
```
##### 4. The height of the population is 170 cm on average with a 10 cm standard deviation. The research sample 40 persons.
1. What is the distribution of the mean of the sampling? Describe the mean and standard deviation of the distribution.

```{r}
distribution <- c(170, 10 / sqrt(40))
names(distribution) <- c("Mean", "S.D.")
distribution
```

2. What is the probability of above 175 cm height on average?

```{r}
percent(1-pnorm(175, mean = 170, sd = 1.581139))
```
