---
title: "5th Homework of 2019 TMU Biostatistics"
author: Bo-Jiang Lin
date: 2019-8-30
output: html_document
---
Taiwan FDA investigated the difference in weight gain of one week infants who received breast milk and A, B, or C formula. They randomly selected 26 infants and recorded the weights (unit: kg) of the infants. The data lists on the following table.
```{r, include=FALSE, echo = FALSE}
library(asbio)
HW5 <- read.csv("D:/HW5.csv",header = TRUE, sep = ",")
ftable(HW5)
```
##### 1. Describe the Null and alternative hypothesis while studying the weight-gain effect of breast milk and A, B, or C formula.

H0: The mean of weight-gain is the same whatever the infants receive breast milk and A, B, or C formula.

Ha: The mean of weight-gain is different between any two groups among the breast milk and A, B, or C formula groups. 

##### 2. List the weight-gain of the breast milk and A, B, or C formula groups by ANOVA table with £\ = 0.05 
Refuse H0 and accept Ha. The formula does affect the weight-gain of infants comparing to breast milk.
```{r}
anova(lm(HW5$weight ~ HW5$Milk))
```
##### 3. Using Kruskal-Wallis test with £\ = 0.05 to investigate the weight-gain between formula and breast milk groups
Refuse H0 and accept Ha. The formula does affect the weight-gain of infants comparing to breast milk.
```{r}
kruskal.test(HW5$weight ~ HW5$Milk)
```
##### 4. If the above results are significant, using Bonferroni adjustment with £\ = 0.05 to test the effect among the A, B, or C formula and breast milk groups.
The weight of infants with formula gains more than others with breast milk. In formula group, The weight of infants with formula-A gain more than others with formula-B.
```{r}
pairwise.t.test(HW5$weight, HW5$Milk,p.adjust.method = "bonferroni")
```