---
title: "Spheroid"
output: html_notebook
author: "Frank"
date: "`r Sys.Date()`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Loading `r version[['version.string']]` and following packages, Set up the connection:

```{r}
library(RODBC)
library(UsingR)
library(ggpubr)
library(ggplot2)
library(ggsignif)
library(dplyr)
library(geepack)
library(ggeasy)
library(ggprism)
library(lme4)
library(knitr)
```

1. Set up driver info and database path

```{r access_path}
DRIVERINFO <- "Driver={Microsoft Access Driver (*.mdb, *.accdb)};"
MDBPATH <- "E:/OneDrive/文件/TMU-DESKTOP-SF2LD60-Surface-Go-Surface-Go.accdb"
PATH <- paste0(DRIVERINFO, "DBQ=", MDBPATH)
```

2. Establish connection

```{r connection}
channel <- odbcDriverConnect(PATH)
```

3. Load data into R dataframe

```{r Load}
df_spheroid <- sqlQuery(channel,"SELECT * FROM Spheroid, Cell WHERE Spheroid.Cell=Cell.識別碼;", stringsAsFactors = FALSE)
df_sample <- sqlQuery(channel,"SELECT * FROM Sample, Collagen_Membrane_Preparation WHERE Sample.Scaffolds=Collagen_Membrane_Preparation.識別碼;")
df_data <- merge(df_spheroid,df_sample,by.x="識別碼.1",by.y = "Cell",all.x = "TRUE")
df_spheroid
```

4. Table on the Data

```{r}
#df_data <- subset.data.frame(df_spheroid, `Cell` == 34)
#[df_data$`Cell` == 25,]

SynthesisMatrix <- df_data[df_data$`Cell` == 185,] %>%
  group_by(`CulturedDate`,`SpheroidDensity`,`Ingredient`,`Status`,`Condition`,`Cell`,`Ancestor`,`Group Name.x`) %>%
  summarise(
    count = sum(!is.na(`Diameter`)),
    mean = mean(`Diameter`, na.rm = TRUE),
    sd = sd(`Diameter`, na.rm = TRUE),
    median = median(`Diameter`, na.rm = TRUE),
    IQR = IQR(`Diameter`, na.rm = TRUE),
    se = sd(`Diameter`, na.rm = TRUE)/sqrt(count)
  )

SynthesisMatrix
```
```{r}
#df_data_single <- subset.data.frame(df_data, `Cell` == 33)
df_data_single <- subset.data.frame(df_data, `Cell` == 185)

ggplot(df_data_single,aes(x=CulturedDate, y=Diameter), ylim=c(0,1000))+
  geom_point(color='gray')+
  geom_line(aes(group=Spheroid),linetype="dotted", color='white')+
  geom_point(  
    mapping = aes(x = CulturedDate, y = mean), data = SynthesisMatrix, colour='red', size=3)+
  geom_line(mapping = aes(x = CulturedDate, y = mean), data = SynthesisMatrix,colour='red', size=2)+
  geom_text(data = SynthesisMatrix, aes(x = CulturedDate, y = mean, label=paste(round(mean,digits = 0))), 
            colour='pink',parse = TRUE, vjust=-1, size=6)+ 
  theme_classic()+
  labs(title = paste("1000 cells/200 μl Spheroid of ",SynthesisMatrix$`Group Name.x`[1]), y="Diameter (μm)", x="Cultured Date (days)")+
  theme(text = element_text(size=19),
        panel.background = element_rect(fill = 'black'),
        plot.background=element_rect(fill = "black",colour = "black"),
        axis.title = element_text(colour = "white"),
        axis.line = element_line(colour = "white",size = 1),
        axis.text = element_text(color = "white"),
        axis.ticks = element_line(colour ="white", size = 2),
        plot.title = element_text(size=20,colour = "white"),
        plot.subtitle = element_text(size = 14, colour = "white"))+
  easy_center_title()
```
```{r fig.width = 15,fig.height = 15}
ggplot(df_spheroid,aes(x=CulturedDate, y=Diameter, group=SpheroidDensity))+
  geom_point(aes(colour=factor(Cell)))+
  geom_line(aes(group=Spheroid),linetype="dotted")+
  facet_wrap(~SpheroidDensity, labeller = "label_both")+ 
  theme_classic()+
  geom_line(mapping = aes(x = CulturedDate, y = mean, group=Cell), data = SynthesisMatrix,colour='red')+
  geom_text(data = SynthesisMatrix, aes(x = CulturedDate, y = mean, label=paste(round(mean,digits = 0))), 
            colour='red',parse = TRUE, vjust=-3, size=2)+
  labs(title = "A549 Spheroid")
```

## Check every density
```{r}
AllMatrix <-   df_data[df_data$CulturedDate <=8 & df_data$SpheroidDensity <= 1000 & df_data$Condition == "Spheroid" & 
#                         df_data$Status != "Contaminated"&
                       (df_data$Status == "CompressedWithCell" | df_data$Status == "UncompressedWithCell") | df_data$Status == "20%Coat" | df_data$Status == "80%Coat",]%>%
#df_data[df_data$`Cell` == 23 | df_data$`Cell` == 25 | df_data$`Cell` == 33,] %>%
  group_by(`CulturedDate`,`Condition`,`Status`,`SpheroidDensity`) %>%
  summarise(
    count = sum(!is.na(`Diameter`)),
    mean = mean(`Diameter`, na.rm = TRUE),
    sd = sd(`Diameter`, na.rm = TRUE),
    median = median(`Diameter`, na.rm = TRUE),
    IQR = IQR(`Diameter`, na.rm = TRUE),
    se = sd(`Diameter`, na.rm = TRUE)/sqrt(count)
  )

AllMatrix
```

```{r}
days <- c(1,2,3,4,5,6,7)
days
```

## Paper style plot - spheroid on ECM
```{r fig.width = 7,fig.height = 4}
#my_xlab <- paste(levels(factor(AllMatrix$CulturedDate)),"\n  ",sep="")
my_xlab <- paste(days)

df_data_All <- subset.data.frame(df_data, CulturedDate <=11 & SpheroidDensity == 1000 & Condition == "Spheroid" & #Status != "Contaminated"& 
                       (Status == "CompressedWithCell" | Status == "UncompressedWithCell"))
# Specify font
windowsFonts(A = windowsFont("Times New Roman")) 

pre <- ggplot(df_data_All,aes(x=CulturedDate, y=Diameter, group=SpheroidDensity, shape=Status,color=Status))+
  geom_point(size=1.5)+
  geom_line(aes(group=interaction(Spheroid,Status)),size=1,linetype="dotted")+
  geom_point(mapping = aes(x = CulturedDate, y = mean), data = AllMatrix, size=15)+
  geom_line(mapping = aes(x = CulturedDate, y = mean, group=Status), data = AllMatrix, size=6)+
#  geom_text(data = AllMatrix, aes(x = CulturedDate, y = mean, label=paste(round(mean,digits = 0))),parse = TRUE, vjust=-2, size=4,fontface = "bold")+ 
#  facet_wrap(~SpheroidDensity, labeller = "label_both")+
  theme_classic()+
  labs( y="Diameter (μm)", x="Cultured Date (days)")+
  scale_y_continuous(guide = "prism_minor",minor_breaks = seq(200, 1800, 100),limits = c(200,2300),expand = c(0,0))+
  scale_x_continuous(labels=my_xlab, breaks = seq(5,11,1))+
#  scale_color_discrete(name = "ECM ",label=c("2.5D","Compressed","Glass","3D","Uncompressed"))+
  theme(axis.line = element_line(size = 2, color = "black"),
        axis.ticks = element_line(size = 2, color = "black"),
        axis.ticks.length=unit(0.4, "cm"),
        prism.ticks.length.y = unit(0.12, "cm"),
        axis.text = element_text(size = 50, color = "black", face = "bold"),
        axis.title = element_text(size = 60, face = "bold"),
        legend.position = "bottom",
        legend.text = element_text(size=35, face = "bold"),
        legend.title = element_text(size=35, face = "bold"),
        axis.line.y = element_blank(),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        axis.title.y = element_blank(),
#        axis.title.x = element_text(hjust = 1),
        axis.title.x = element_blank(),
        text = element_text(family ="A"))
pre

growth <- ggplot(df_data_All,aes(x=CulturedDate, y=Diameter, group=SpheroidDensity, shape=Status,color=Status))+
  geom_point(size=1)+
  geom_line(aes(group=interaction(Spheroid,Status)),size=0.5,linetype="dotted")+
  geom_point(mapping = aes(x = CulturedDate, y = mean), data = AllMatrix, size=5)+
  geom_line(mapping = aes(x = CulturedDate, y = mean, group=Status), data = AllMatrix, size=1.5)+
#  geom_text(data = AllMatrix, aes(x = CulturedDate, y = mean, label=paste(round(mean,digits = 0))),parse = TRUE, vjust=-2, size=4,fontface = "bold")+ 
#  facet_wrap(~SpheroidDensity, labeller = "label_both")+
  theme_classic()+
  labs( y="Diameter (μm)", x="Cultured Date (days)", title = "Spheroid Expansion")+
  scale_y_continuous(expand = c(0,0), breaks = seq(0,2000,200))+
  scale_x_continuous(labels=my_xlab, breaks = seq(5,11,1))+
#  scale_color_discrete(name = "ECM ",label=c("2.5D","Compressed","Glass","3D","Uncompressed"))+
  theme(axis.line = element_line(size = 2, color = "black"),
        axis.ticks = element_line(size = 2, color = "black"),
        axis.ticks.length=unit(0.4, "cm"),
#        prism.ticks.length.y = unit(0.12, "cm"),
        axis.text = element_text(size = 20, color = "black", face = "bold"),
        axis.title = element_text(size = 20, face = "bold",hjust = 1),
        legend.position = "none",
        legend.text = element_text(size=25, face = "bold"),
        legend.title = element_text(size=25, face = "bold"),
#        axis.line.y = element_blank(),
#        axis.text.y = element_blank(),
#        axis.ticks.y = element_blank(),
#        axis.title.y = element_blank(),
#        axis.title.x = element_text(hjust = 1),
#        axis.title.x = element_blank(),
        text = element_text(family ="A"),
        plot.title = element_text(size = 25, face = "bold"))+
  easy_center_title()

growth
```
```{r fig.width = 7,fig.height = 3.5}
ggplot(AllMatrix,aes(x=CulturedDate, y=mean, group=SpheroidDensity, shape=Status,color=Status))+
  geom_point(mapping = aes(x = CulturedDate, y = mean), data = AllMatrix, size=5)+
  geom_line(mapping = aes(x = CulturedDate, y = mean, group=Status), data = AllMatrix, size=1.5)+
  geom_errorbar(aes(ymin=mean-se, ymax=mean+se), width=0.2,size=2)+
#  geom_text(data = AllMatrix, aes(x = CulturedDate, y = mean, label=paste(round(mean,digits = 0))),parse = TRUE, vjust=-2, size=4,fontface = "bold")+ 
#  facet_wrap(~SpheroidDensity, labeller = "label_both")+
#  theme_classic()+
  theme_bw()+
  border(size = 3)+
  labs( y="Diameter (μm)", x="Cultured Date (days)", 
#        title = "Spheroid Expansion"
        )+
  scale_y_continuous(breaks = seq(0,2000,200))+
  scale_x_continuous(labels=my_xlab, breaks = seq(5,11,1))+
  scale_color_discrete(name = "ECM ",label=c("20%Coat","80%Coat","Compressed","Uncompressed",""))+
  scale_shape_discrete(name = "ECM ",label=c("20%Coat","80%Coat","Compressed","Uncompressed",""))+
  theme(
#        axis.line = element_line(size = 2, color = "black"),
        axis.ticks = element_line(size = 2, color = "black"),
        axis.ticks.length=unit(0.4, "cm"),
#        prism.ticks.length.y = unit(0.12, "cm"),
        axis.text = element_text(size = 26, color = "black", face = "bold"),
        axis.title = element_text(size = 24, face = "bold"),
        legend.position = "top",
        legend.text = element_text(size=14, face = "bold"),
        legend.title = element_text(size=14, face = "bold"),
#        axis.line.y = element_blank(),
#        axis.text.y = element_blank(),
#        axis.ticks.y = element_blank(),
#        axis.title.y = element_blank(),
#        axis.title.x = element_text(hjust = 1),
#        axis.title.x = element_blank(),
        text = element_text(family ="A"),
        plot.title = element_text(size = 25, face = "bold"),
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank())+
  easy_center_title()
```
### Black

```{r fig.width = 10,fig.height = 15}
ggplot(AllMatrix,aes(x=CulturedDate, y=mean, group=SpheroidDensity, shape=Status,color=Status))+
  geom_point(mapping = aes(x = CulturedDate, y = mean), data = AllMatrix, size=15)+
  geom_line(mapping = aes(x = CulturedDate, y = mean, group=Status), data = AllMatrix, size=5)+
  geom_errorbar(aes(ymin=mean-se, ymax=mean+se), width=0.4, size=4)+
#  geom_text(data = AllMatrix, aes(x = CulturedDate, y = mean, label=paste(round(mean,digits = 0))),parse = TRUE, vjust=-2, size=4,fontface = "bold")+ 
#  facet_wrap(~SpheroidDensity, labeller = "label_both")+
  theme_classic()+
  labs( y="Mean Diameter (μm)", x="Cultured Date (days)", title = "Time course of change \n in the diameter of \n the A549 spheroid for 4 days"
        )+
  scale_y_continuous(expand = c(0,0), breaks = seq(0,2000,200))+
  scale_x_continuous(labels=my_xlab, breaks = seq(5,11,1))+
#  scale_color_discrete(name = "ECM ",label=c("2.5D","Compressed","Glass","3D","Uncompressed"))+
  theme(axis.line = element_line(size = 5, color = "white"),
        axis.ticks = element_line(size = 5, colour ="white"),
        axis.ticks.length=unit(0.5, "cm"),
#        prism.ticks.length.y = unit(0.12, "cm"),
        axis.text = element_text(size = 50, color = "white", face = "bold"),
        axis.title = element_text(size = 38, face = "bold",hjust = 1,colour = "white"),
        legend.position = "top",
        legend.text = element_text(size=18, face = "bold",colour = 'white'),
        legend.title = element_text(size=20, face = "bold"),
#        axis.line.y = element_blank(),
#        axis.text.y = element_blank(),
#        axis.ticks.y = element_blank(),
#        axis.title.y = element_blank(),
#        axis.title.x = element_text(hjust = 1),
#        axis.title.x = element_blank(),
        text = element_text(family ="A"),
        plot.title = element_text(size = 40, face = "bold",colour = "white"),
        panel.background = element_rect(fill = 'black'),
        plot.background=element_rect(fill = "black",colour = "black"),
        legend.background = element_rect(fill = 'black'))+
  easy_center_title()
```


```{r}
samplesize <- ggtexttable(table(df_data_All$Status,df_data_All$CulturedDate), theme = ttheme("light",base_size = 22))
samplesize
```


#### Paper style plot - Preparation
```{r}
df_data_prep <-  subset.data.frame(df_data, CulturedDate <= 4 & SpheroidDensity == 0)

SingMatrix <-   df_data_prep %>%
  group_by(`CulturedDate`,`Condition`,`Status`,`SpheroidDensity`) %>%
  summarise(
    count = sum(!is.na(`Diameter`)),
    mean = mean(`Diameter`, na.rm = TRUE),
    sd = sd(`Diameter`, na.rm = TRUE),
    median = median(`Diameter`, na.rm = TRUE),
    IQR = IQR(`Diameter`, na.rm = TRUE),
    se = sd(`Diameter`, na.rm = TRUE)/sqrt(count)
  )

SingMatrix
```


```{r}
my_xlab <- paste(SingMatrix$`CulturedDate`,"\n(",SingMatrix$count,")",sep="")

post <- ggplot(df_data_prep,aes(x=CulturedDate, y=Diameter))+
  geom_point(size=2.3, color="gray")+
  geom_line(aes(group=Spheroid),linetype="dotted", size=2, color="gray")+
  geom_point(mapping = aes(x = CulturedDate, y = mean), data = SingMatrix, size=7)+
  geom_line(mapping = aes(x = CulturedDate, y = mean), data = SingMatrix, size=6)+
  theme_classic()+
  labs( y="Diameter (μm)", x=" ")+
  scale_y_continuous(guide = "prism_minor",minor_breaks = seq(200, 1800, 100),limits = c(200,2300),expand = c(0,0))+
  theme(axis.line = element_line(size = 2, color = "black"),
        axis.ticks = element_line(size = 2, color = "black"),
        axis.ticks.length=unit(0.4, "cm"),
        prism.ticks.length.y = unit(0.2, "cm"),
        axis.text = element_text(size = 50, color = "black", face = "bold"),
#        axis.title.x = element_text(size = 100, face = "bold"),
        axis.title.y = element_text(size=60, face = "bold"),
        text = element_text(family ="A"))+
  scale_x_continuous(labels=my_xlab)

post
```
#### Combined
```{r  fig.width = 30,fig.height = 10}
figuretot <- ggarrange(post,pre, ncol = 2, nrow = 1, widths = c(3,4),common.legend = TRUE, legend = "top")
figuretot
#annotate_figure(figuretot,bottom = text_grob("Cultured Date (days)",size = 60,hjust = 1.4, vjust = -1,  face = "bold", family = "A"))
```


#### plot the density of spheroid
```{r fig.width = 22,fig.height = 5}
#df_data_All <- subset.data.frame(df_data, `Cell` == 23 | `Cell` == 25 | `Cell` == 33)
#df_data_All <- subset.data.frame(df_data, CulturedDate <=11 & df_data$SpheroidDensity == 1000 & Condition == "Spheroid" & Status != "Contaminated")
my_xlab <- paste(SingMatrix$`CulturedDate`,"\n(N=",SingMatrix$count,")",sep="")

ggplot(df_data_prep,aes(x=CulturedDate, y=Diameter))+
  geom_point(color="dimgrey")+
  geom_line(aes(group=Spheroid),linetype="dotted", size=1,color="dimgrey")+
  geom_point(mapping = aes(x = CulturedDate, y = mean), data = SingMatrix, size=7, color="red")+
  geom_line(mapping = aes(x = CulturedDate, y = mean), data = SingMatrix, size=6, color="red")+
#  geom_point(  
#    mapping = aes(x = CulturedDate, y = mean), data = AllMatrix, size=3)+
#  geom_line(mapping = aes(x = CulturedDate, y = mean, group=Status), data = AllMatrix, size=2)+
  geom_text(data = SingMatrix, aes(x = CulturedDate, y = mean, label=paste(round(mean,digits = 0))),parse = TRUE, vjust=-1, size=14,fontface = "bold", color="red")+ 
  theme_classic()+
  labs( y="Diameter (μm)", x="Cultured Date (days)")+
  scale_y_continuous(expand = c(0,0))+
  theme(text = element_text(size=40),
        panel.background = element_rect(fill = 'black'),
        plot.background=element_rect(fill = "black",colour = "black"),
        axis.title = element_text(colour = "white"),
        axis.line = element_line(colour = "white",size = 1),
        axis.text = element_text(color = "white"),
        axis.ticks = element_line(colour ="white", size = 2),
        plot.title = element_text(size=20,colour = "white"),
        legend.background = element_rect(fill = 'black'),
        legend.text = element_text(colour = 'white'),
        legend.title = element_blank(),
        legend.position = "top")+
  ylim(0,1000)+
  scale_x_continuous(labels=my_xlab)
```


## Growth among all ECM
```{r}
#df_data_reg <- subset.data.frame(df_data, `Cell` == 37 |`Cell` == 38 | `Cell` == 40 |`Cell` == 41)

geerun <- geeglm(Diameter ~ factor(CulturedDate)+factor(Status)+factor(CulturedDate)*factor(Status), id=factor(Spheroid), data=df_data_All, family=gaussian , corstr = "ar1")
summary(geerun)
anova(geerun)
```
### GLMM
```{r}
glmm <- glmer(Diameter ~ factor(CulturedDate)+factor(Status)+factor(Status)*factor(CulturedDate)+ (1|Spheroid), data = df_data_All, family=Gamma)
summary(glmm)
```


## Plot among all culturation on different ECM
```{r fig.width = 20,fig.height = 8}
ggplot(df_data_All,aes(x=CulturedDate, y=Diameter, group=SpheroidDensity, color=Status))+
  geom_point(size=1)+
  geom_line(aes(group=Spheroid),size=0.2)+
  geom_point(mapping = aes(x = CulturedDate, y = mean), data = AllMatrix, size=7)+
  geom_line(mapping = aes(x = CulturedDate, y = mean, group=Status), data = AllMatrix, size=6)+
  geom_text(data = AllMatrix, aes(x = CulturedDate, y = mean, label=paste(round(mean,digits = 0))),parse = TRUE, vjust=-1, size=11,fontface = "bold")+ 
  theme_classic()+
  scale_x_continuous(breaks = seq(5,11,1))+
  labs( y="Diameter (μm)", x="Cultured Date (days)")+
  theme(text = element_text(size=40),
        panel.background = element_rect(fill = 'black'),
        plot.background=element_rect(fill = "black",colour = "black"),
        axis.title = element_text(colour = "white"),
        axis.line = element_line(colour = "white",size = 1),
        axis.text = element_text(color = "white"),
        axis.ticks = element_line(colour ="white", size = 2),
        plot.title = element_text(size=20,colour = "white"),
        legend.background = element_rect(fill = 'black'),
        legend.text = element_text(colour = 'white'),
        legend.title = element_blank(),
        legend.position = "top")+
  ylim(300,2500)
```


## Close and remove channel

```{r}
close(channel)
```


### RationOver4days
```{r}
Fourdays <- subset.data.frame(df_spheroid, CulturedDate==4)
for (a in 1:length(Fourdays$Spheroid)) {
  df_spheroid[which(df_spheroid$Spheroid == Fourdays[a,]$Spheroid),]$fourdaysRatio <- df_spheroid$Diameter[which(df_spheroid$Spheroid == Fourdays[a,]$Spheroid)]/Fourdays[a,]$Diameter
}
head(df_spheroid)
```


### Update the Growth Ration over 4days
```{r}
sqlUpdate(channel,df_spheroid[,1:15],tablename = "Spheroid", index = "識別碼")
```

### The synthesis matrix of Growth ratio
```{r}
FourDaysMatrix <-   df_data[df_data$CulturedDate <=20 & df_data$SpheroidDensity <= 1000 & df_data$Condition == "Spheroid" & 
#                         df_data$Status != "Contaminated"&
                       (df_data$Status == "CompressedWithCell" | df_data$Status == "UncompressedWithCell"),]%>%
#| df_data$Status == "20%Coat" | df_data$Status == "80%Coat",]%>%
#df_data[df_data$`Cell` == 23 | df_data$`Cell` == 25 | df_data$`Cell` == 33,] %>%
  group_by(`CulturedDate`,`Condition`,`Status`,`SpheroidDensity`) %>%
  summarise(
    count = sum(!is.na(`fourdaysRatio`)),
    mean = mean(`fourdaysRatio`, na.rm = TRUE),
    sd = sd(`fourdaysRatio`, na.rm = TRUE),
    median = median(`fourdaysRatio`, na.rm = TRUE),
    IQR = IQR(`fourdaysRatio`, na.rm = TRUE),
    se = sd(`fourdaysRatio`, na.rm = TRUE)/sqrt(count)
  )

FourDaysMatrix
```

### The plot of growth ratio
```{r}
ggplot(FourDaysMatrix,aes(x=CulturedDate, y=mean, group=SpheroidDensity, shape=Status,color=Status))+
  geom_point(mapping = aes(x = CulturedDate, y = mean), data = FourDaysMatrix, size=5)+
  geom_line(mapping = aes(x = CulturedDate, y = mean, group=Status), data = FourDaysMatrix, size=1.5)+
  geom_errorbar(aes(ymin=mean-se, ymax=mean+se), width=0.2,size=2)+
#  geom_text(data = AllMatrix, aes(x = CulturedDate, y = mean, label=paste(round(mean,digits = 0))),parse = TRUE, vjust=-2, size=4,fontface = "bold")+ 
#  facet_wrap(~SpheroidDensity, labeller = "label_both")+
#  theme_classic()+
  theme_bw()+
  border(size = 3)+
  labs( y="Growth ratio \n (Diameter/initial Diameter)", x="Cultured Date (days)", 
#        title = "Spheroid Expansion"
        )+
#  scale_y_continuous(breaks = seq(0,2000,200))+
#  scale_x_continuous(labels=my_xlab, breaks = seq(5,11,1))+
#  scale_color_discrete(name = "ECM ",label=c("20%Coat","80%Coat","Compressed","Uncompressed",""))+
#  scale_shape_discrete(name = "ECM ",label=c("20%Coat","80%Coat","Compressed","Uncompressed",""))+
  theme(
#        axis.line = element_line(size = 2, color = "black"),
        axis.ticks = element_line(size = 2, color = "black"),
        axis.ticks.length=unit(0.4, "cm"),
#        prism.ticks.length.y = unit(0.12, "cm"),
        axis.text = element_text(size = 24, color = "black", face = "bold"),
        axis.title = element_text(size = 20, face = "bold"),
        legend.position = "top",
        legend.text = element_text(size=14, face = "bold"),
        legend.title = element_text(size=14, face = "bold"),
#        axis.line.y = element_blank(),
#        axis.text.y = element_blank(),
#        axis.ticks.y = element_blank(),
#        axis.title.y = element_blank(),
#        axis.title.x = element_text(hjust = 1),
#        axis.title.x = element_blank(),
        text = element_text(family ="A"),
        plot.title = element_text(size = 25, face = "bold"),
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank())+
  easy_center_title()
```
```{r}
growthpattern <- subset.data.frame(df_data,(CulturedDate==11)&(df_data$Status == "UncompressedWithCell"| df_data$Status == "CompressedWithCell"))
```
```{r}
shapiro.test(growthpattern$day5Ratio)
```

```{r}
#compare_means(fourdaysRatio ~ Status,growthpattern,method = "t.test")
t.test(day5Ratio ~ Status,data = growthpattern)
```

#### Ratio over Day 5
```{r}
Fourdays <- subset.data.frame(df_spheroid, CulturedDate==5)
for (a in 1:length(Fourdays$Spheroid)) {
  df_spheroid[which(df_spheroid$Spheroid == Fourdays[a,]$Spheroid),]$day5Ratio <- df_spheroid$Diameter[which(df_spheroid$Spheroid == Fourdays[a,]$Spheroid)]/Fourdays[a,]$Diameter
}
head(df_spheroid)
```
#### The synthesis matrix of Growth ratio
```{r}
Day5Matrix <-   df_data[df_data$CulturedDate <=11 & df_data$SpheroidDensity == 1000 & df_data$Condition == "Spheroid" &
#                         df_data$Status != "Contaminated"&
                       (df_data$Status == "CompressedWithCell" | df_data$Status == "UncompressedWithCell"),]%>%
#| df_data$Status == "20%Coat" | df_data$Status == "80%Coat",]%>%
#df_data[df_data$`Cell` == 23 | df_data$`Cell` == 25 | df_data$`Cell` == 33,] %>%
  group_by(`CulturedDate`,`Condition`,`Status`,`SpheroidDensity`) %>%
  summarise(
    count = sum(!is.na(`day5Ratio`),na.rm = TRUE),
    mean = mean(`day5Ratio`, na.rm = TRUE),
    sd = sd(`day5Ratio`, na.rm = TRUE),
    median = median(`day5Ratio`, na.rm = TRUE),
    IQR = IQR(`day5Ratio`, na.rm = TRUE),
    se = sd(`day5Ratio`, na.rm = TRUE)/sqrt(count)
  )

Day5Matrix
```
### The plot of growth ratio
```{r}
my_xlab <- paste(days)

ggplot(Day5Matrix,aes(x=CulturedDate, y=mean, group=SpheroidDensity, shape=Status,color=Status))+
  geom_point(mapping = aes(x = CulturedDate, y = mean), data = Day5Matrix, size=5)+
  geom_line(mapping = aes(x = CulturedDate, y = mean, group=Status), data = Day5Matrix, size=1.5)+
  geom_errorbar(aes(ymin=mean-se, ymax=mean+se), width=0.2,size=2)+
#  geom_text(data = AllMatrix, aes(x = CulturedDate, y = mean, label=paste(round(mean,digits = 0))),parse = TRUE, vjust=-2, size=4,fontface = "bold")+ 
#  facet_wrap(~SpheroidDensity, labeller = "label_both")+
#  theme_classic()+
  theme_bw()+
  border(size = 3)+
  labs( y= "Growth ratio \n (Diameter/initial Diameter)", x="Cultured Date (days)", 
#        title = "Spheroid Expansion"
        )+
#  scale_y_continuous(breaks = seq(0,2000,200))+
  scale_x_continuous(labels=my_xlab, breaks = seq(5,11,1))+
#  scale_color_discrete(name = "ECM ",label=c("20%Coat","80%Coat","Compressed","Uncompressed",""))+
#  scale_shape_discrete(name = "ECM ",label=c("20%Coat","80%Coat","Compressed","Uncompressed",""))+
  theme(
#        axis.line = element_line(size = 2, color = "black"),
        axis.ticks = element_line(size = 2, color = "black"),
        axis.ticks.length=unit(0.4, "cm"),
#        prism.ticks.length.y = unit(0.12, "cm"),
        axis.text = element_text(size = 24, color = "black", face = "bold"),
        axis.title = element_text(size = 20, face = "bold"),
        legend.position = "top",
        legend.text = element_text(size=14, face = "bold"),
        legend.title = element_text(size=14, face = "bold"),
#        axis.line.y = element_blank(),
#        axis.text.y = element_blank(),
#        axis.ticks.y = element_blank(),
#        axis.title.y = element_blank(),
#        axis.title.x = element_text(hjust = 1),
#        axis.title.x = element_blank(),
        text = element_text(family ="A"),
        plot.title = element_text(size = 25, face = "bold"),
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank())+
  easy_center_title()
```